Modelling state-switching functional data with hidden Markov models: supplement B (simulation study)

### 2021-06-24 Report/Supp_Sim.tex
Update Simulation Study in Report
Update Report

% Title, authors, affiliations
\title{Modelling state-switching functional data with hidden Markov models: supplementary material (simulation study)}%\query{Q1}
\date{}
\author{BlindedA, BlindedB}%\authorref{1}\thanksref{*}}
%\author{BlindedB}%\authorref{2}}
%\affiliation[1]{Author affiliations will go here in the accepted manuscript, but do NOT include them in your initial submission because it must be anonymous.}
%\affiliation[2]{Second Affiliation}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the CarHHMM-DFT and correspond to both dive types. The red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the HHMM-DFT and correspond to both dive types. The red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the CarHHMM and correspond to both dive types. The red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$ and $\hat \sigma^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$ and $\sigma^*_A$ for both subdive states. These estimates are for the HHMM-DFT. Note that the HHMM-DFT assumes no auto-correlation in $\Zone_{t,\tilde t^*}$, so $\hat \phi_A^{*(\cdot,i^*)}$ is absent from these plots.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM. 
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}

@@

@@

                            &                               & 3                                & $9787.1$                         & $17.2$ $(p=0.718)$           & $1060.5$                            & $262.1 \pm 97.120$                             \\
                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.849$                         & $-0.001$ $(p=0.991)$         & $0.989$                             & $0.658 \pm 0.088$                             \\
                            &                               & 2                                & $514.21$                         & $-2.47$ $(p=0.010)$          & $21.43$                             & $9.74 \pm 0.81$                             \\
                            &                               & 3                                & $14430$                          & $-33$ $(p=0.647)$            & $1596$                              & $262 \pm 97$                             \\ \hline

@@

                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.800$                         & $-0.050$ $(p=0.351)$         & $1.192$                             & $0.679 \pm 0.100$                             \\
                            &                               & 2                                & $513.26$                         & $-3.42$ $(p=0.001)$          & $22.60$                             & $10.75 \pm 1.21$                             \\
                            &                               & 3                                & $11459$                          & $-3004$ $(p=0.000)$          & $1739$                              & $198 \pm 77$                             \\ \hline

@@

                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.890$                         & $0.040$ $(p=0.401)$          & $1.058$                             & $0.661 \pm 0.093$                             \\
                            &                               & 2                                & $515.23$                         & $-1.45$ $(p=0.125)$          & $21.09$                             & $9.64 \pm 0.92$                             \\
                            &                               & 3                                & $14438$                          & $-25$ $(p=0.740)$            & $1661$                              & $280 \pm 136$                             \\

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the HHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}

>>>>

% Title, authors, affiliations
\title{Modelling state-switching functional data with hidden Markov models: supplement B (simulation study)}%\query{Q1}
\date{}
\author{BlindedA, BlindedB}%\authorref{1}\thanksref{*}}
%\author{BlindedB}%\authorref{2}}
%\affiliation[1]{Author affiliations will go here in the accepted manuscript, but do NOT include them in your initial submission because it must be anonymous.}
%\affiliation[2]{Second Affiliation}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the CarHHMM-DFT and correspond to both dive types. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the HHMM-DFT and correspond to both dive types. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the CarHHMM and correspond to both dive types. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$ and $\hat \sigma^*_A$) for each subdive state. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu^*_A$ and $\sigma^*_A$ for both subdive states. These estimates are for the HHMM-DFT. Note that the HHMM-DFT assumes no auto-correlation in $\Zone_{t,\tilde t^*}$, so $\hat \phi_A^{*(\cdot,i^*)}$ is absent from these plots.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM. 
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \begin{center}
        \scalebox{0.75}{
        \bgroup
        \centering
        \def\arraystretch{1.5}

@@

                            &                               & 3                                & $9787.1$                         & $17.2$ $(p=0.718)$          & $1060.5$                             & $262.1 \pm 97.1$                             \\
                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.849$                         & $-0.001$ $(p=0.991)$          & $0.989$                             & $0.652 \pm 0.094$                             \\
                            &                               & 2                                & $514.21$                         & $-2.47$ $(p=0.010)$          & $21.43$                             & $11.41 \pm 0.95$                             \\
                            &                               & 3                                & $14430$                         & $-33$ $(p=0.647)$          & $1596$                             & $303 \pm 166$                             \\ \hline

@@

                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.800$                         & $-0.050$ $(p=0.351)$          & $1.192$                             & $0.676 \pm 0.104$                             \\
                            &                               & 2                                & $513.26$                         & $-3.42$ $(p=0.001)$          & $22.60$                             & $12.50 \pm 1.30$                             \\
                            &                               & 3                                & $11459$                         & $-3004$ $(p=0.000)$          & $1739$                             & $280 \pm 136$                             \\ \hline

@@

                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.890$                         & $0.040$ $(p=0.401)$          & $1.058$                             & $0.656 \pm 0.101$                             \\
                            &                               & 2                                & $515.23$                         & $-1.45$ $(p=0.125)$          & $21.09$                             & $11.37 \pm 0.99$                             \\
                            &                               & 3                                & $14438$                         & $-25$ $(p=0.740)$          & $1661$                             & $303 \pm 166$                             \\

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the HHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The white star represents the mean of all maximum likelihood estimates and the red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}
